---
title: "705 Homework 7"
author: "Graham"
date: "November 3, 2019"
output:
  pdf_document: default
  html_document: default
---


# 1

Writing 

$$S = DRD$$

We can use the definition of $D$ and $R$ to see 

$$S = \begin{pmatrix} s_y & 0' \\ 0 &  D_x \end{pmatrix}\begin{pmatrix} 1 & r'_{yx} \\ r_{yx} &  R_{xx} \end{pmatrix}\begin{pmatrix} s_y & 0' \\ 0 &  D_x \end{pmatrix}$$

$$S = \begin{pmatrix} s_y & s_yr'_{yx} \\ D_xr_{yx} &  D_xR_{xx} \end{pmatrix}\begin{pmatrix} s_y & 0' \\ 0 &  D_x \end{pmatrix}$$
$$S = \begin{pmatrix} s_y^2 &  s_yr'_{yx}D_x \\ s_yD_xr_{yx} &  D_xR_{xx}D_x \end{pmatrix}$$




# 2 

# a 

We have $n-1$ choices for the first bootstrap sample out of a total of $n$ choices. This gives us 

$$\frac{n-1}{n} = 1 - 1/n$$


# b

By symmetry, the same as part a.

# c

Each bootstrap sample is drawn independently so this probability is 

$$(1-1/n)^n$$


# d 
```{r}
n <- 5
((1/n))^n
```
# e
```{r}
n <- 100
((1/n))^n
```


# f 
```{r}
n <- 100000
((1/n))^n
```

# g
```{r}
prob_jth = function(n){ (1/n)^n }
x = 1:10000
y = sapply(x,prob_jth)
plot(x,y,type='l')

```

# h

```{r}
store=rep(NA,10000)
for(i in 1:10000){
  store[i]=sum(sample(1:100,rep=TRUE)==4)>0
}

mean(store)
```


This means that on average, there is a 64 percent probability that the j-th observation is in the bootstrap sample.


# 3

We repeatedly sample from the original dataset to obtain an estimate of the model parameters, $\theta$. We then compute 

$$\hat{y}^{(i)} \sim f(Y|X,\theta^{(i)})$$

This gives us an empirical distribution we can take the sample variance of 


$$Var(\hat{y}) = \frac{1}{n-1}\sum_{i}(\hat{y}^{(i)} - \bar{\hat{y}})^2$$






