---
title: "KCDE With Backfill"
author: "Graham Casey Gibson"
date: "10/13/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Here we introduce the KCDETD package for R. The KCDE method uses an estimate of the conditional distribution of a time-series given:
- The last 4 observed points in the time series. 
- The value observed last season. 
- The epiweek used to forecast.



```{r, message=FALSE,results='hide',echo=FALSE}
library(devtools)
library(dplyr)
#devtools::install_github("https://github.com/reichlab/cdcfluutils",force = T)
library(KCDETD)
library(tsfknn)
library(sarimaTD)


state_data <-read.csv("../data/state_data.csv")
unique_states <- unique(state_data$region)
    nsim <- 1000

fs_mat_kcde <- matrix(NA,nrow=100*length(unique_states),ncol=4)
fs_mat_sarima <- matrix(NA,nrow=100*length(unique_states),ncol=4)


ls_index <- 1
for (state in sample(unique_states,10)){
  ma_data <- state_data[state_data$region == state,]
  for (first_test_index in 200:220){
    kcde_fit <- fit_kcde(ma_data$unweighted_ili[1:(first_test_index-1)],
                         ma_data$season_week[1:(first_test_index-1)],
                         ts_frequency = 52,
                         h=52,transformation = "none")
    
    preds <- simulate_with_backfill(kcde_fit,nsim,newX = ma_data$unweighted_ili[1:(first_test_index-1)],ts_frequency = 52,
                                            h=52,
                                            epiweek = ma_data$season_week[first_test_index-1],
                                            season=ma_data$season[first_test_index-1],region="ma",seed = 1)
    
    
    sarima_fit <- fit_sarima(ma_data$unweighted_ili[1:(first_test_index-1)],52,transformation = "box-cox",seasonal_difference = TRUE)
    
    sarima_pred <- 
  simulate(
    object = sarima_fit,
    nsim = 1000,
    seed = 1,
    newdata = ma_data$unweighted_ili[1:(first_test_index-1)],
    h = 52
  )
    truth <- ma_data[first_test_index:(first_test_index+3),]$unweighted_ili
    for (h in 1:4){
      fs_mat_kcde[ls_index,h] <- sum(round(preds[,ncol(preds) -4 + h],2) == round(truth[h],2))/1000
      fs_mat_sarima[ls_index,h] <- sum(round(sarima_pred[,ncol(sarima_pred) -4 + h],2) == round(truth[h],2))/1000
    }
    ls_index <- ls_index+1
  }
}  
#ggplot(data=data.frame(y=c(t(preds)),x=rep(1:ncol(preds),1000),group=rep(1:1000,each=ncol(preds))),aes(x=x,y=y,group=group)) + geom_line() + geom_line(data=ma_data[first_test_index:(first_test_index+3),],aes(x=ncol(preds)-4+ 1:4,y=unweighted_ili,group=1,col='truth'))
```

## Data

To begin we look at a classic infectious disease time series data set: influenza-like-illness as reported by the CDC in Colorado. 



```{r}
library(devtools)
library(dplyr)
library(KCDETD)
library(jsonlite)
library(ggplot2)
state_data <-read.csv("../data/state_data.csv")
co_data <- state_data[state_data$region == "Colorado",]
ggplot(co_data,aes(x=week_start,y=unweighted_ili,group=1)) + geom_line()
```


We then fit the KCDE model to the available data using the `fit_kcde` method after choosing an evaluation point. 


```{r, results='hide',echo=FALSE}
  nsim <- 1000

kcde_fit <- fit_kcde(co_data$unweighted_ili[1:(first_test_index-1)],co_data$season_week[1:(first_test_index-1)],52,h=4)
```


```{r,eval=FALSE}
nsim <- 1000

kcde_fit <- fit_kcde(co_data$unweighted_ili[1:(first_test_index-1)],
                     co_data$season_week[1:(first_test_index-1)],
                     52,
                     h=4)
```


Finally we generate predictions using the fitted model on the same data used to train the model. 

```{r}
preds <- simulate_with_backfill(kcde_fit,
                                nsim,
                                newX = co_data$unweighted_ili[1:(first_test_index-1)],
                                newt = co_data$season_week[1:(first_test_index-1)],
                                ts_frequency = 52,
                                h=4,
                                epiweek = co_data$season_week[first_test_index-1],
                                season=co_data$season[first_test_index-1],
                                region="co")
                                      

```

Finally, we plot the results
```{r}
library(ggplot2)
ggplot(data=data.frame(y=c(t(preds)),x=rep(1:ncol(preds),1000),group=rep(1:1000,each=ncol(preds))),aes(x=x,y=y,group=group)) + geom_line() + geom_line(data=ma_data[first_test_index:(first_test_index+3),],aes(x=ncol(preds)-4+ 1:4,y=unweighted_ili,group=1,col='truth'))
```
